Binning Strategies and Related Loss for Large Data

### 2015-03-03 Paper.Rnw
Spatial loss subsection start

\ktm{The following \textit{numerical, visual and freq} loss descriptions are from the old list and will be removed: }
\begin{itemize}
\item {\it Numerical Loss}, $L^\text{N}$, occurs when points in the data set are reduced to a single points at the bin means.  Allocating points to the numerical center, or the mean of the data corresponding to that bin, causes a loss of information about the exact location of the points.

>>>>

\subsection{Spatial Loss}

\ktm{When the individual points of a scatterplot are collapsed to bin centers to be displayed as tiles in a binned scatterplot there is a loss of the location information.  This can be expressed as the Euclidean distance between points and the visual center of the tiles (i.e. the bin centers). Note that other distance metrics could be used, but the euclidean distance has a desirable interpretability in $\mathbb{R}^2$. The spatial loss for the $i^{th}$ observation, $L_i^S$ and the total spatial loss, $L^S$ are defined as}
%
\begin{eqnarray}\label{indspatloss}
L_i^S = \sqrt{ (x_i-b_X(x_i))^2 + (y_i-b_Y(y_i))^2 }
\end{eqnarray}
%
\begin{eqnarray}\label{totspatloss}
L^S = \sum_{i=1}^{n} L_i^S
\end{eqnarray}  
%

\subsection{Old Loss Definitions (to be removed)}
\ktm{The following \textit{numerical, visual and freq} loss descriptions are from the old list and will be removed: }
\begin{itemize}
\item {\it Numerical Loss}, $L^\text{N}$, occurs when points in the data set are reduced to a single points at the bin means.  Allocating points to the numerical center, or the mean of the data corresponding to that bin, causes a loss of information about the exact location of the points.
